Whole-chromosome pairwise alignment using a hierarchical wavefront algorithm

### 2021-05-31 manuscript/main.tex
added the methods; cleaning

    \section{Approach}

    Equation~(\ref{eq:01}) Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text
    .....

    \begin{methods}
        \section{Methods}

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text
        text\vspace*{1pt}

        \begin{itemize}
            \item for bulleted list, use itemize
            \item for bulleted list, use itemize
            \item for bulleted list, use itemize\vspace*{1pt}
        \end{itemize}

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text\vadjust{\newpage}.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.

        \subsection{This is subheading}

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text
        text. Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.

        \subsubsection{This is subsubheading}

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text\break
        text text

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text
        textText Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.

        \enlargethispage{6pt}

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.

        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text
        Text Text Text Text Text Text Text Text Text Text Text Text Text
        Text Text Text Text Text Text Text Text.
        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
        Text Text Text Text Text Text Text Text Text Text Text.
        \citealp{Boffelli03} might want to know about text text text text

        \begin{table}[!t]
            \processtable{This is table caption\label{Tab:01}} {\begin{tabular}{@{}llll@{}}
                                                                    \toprule head1 &
                                                                    head2 & head3 & head4 \\\midrule
                                                                    row1 & row1 & row1 & row1 \\
                                                                    row2 & row2 & row2 & row2 \\
                                                                    row3 & row3 & row3 & row3 \\
                                                                    row4 & row4 & row4 & row4 \\\botrule
            \end{tabular}}{This is a footnote}
        \end{table}

    \end{methods}

    \begin{figure}[!tpb]%figure1
        \fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{235pt}
                                        \vbox to 100pt{\vfill\hbox to
                                        235pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
        \end{minipage}}
%\centerline{\includegraphics{fig01.eps}}
        \caption{Caption, caption.}\label{fig:01}
    \end{figure}

@@

    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text
    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text
    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text

    \subsection{Test1}

    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text
    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text
    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text

@@

    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text
    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text
    Text Text Text Text Text Text Text Text Text Text.

    Table~\ref{Tab:01} shows that Text Text Text Text Text Text Text
    Text Text Text Text. Figure~2\vphantom{\ref{fig:02}} shows that
    the above method Text Text. Text Text Text Text Text Text Text
    Text Text. Figure~2\vphantom{\ref{fig:02}} shows that the above
    method Text Text. Text Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text.

    \section{Conclusion}

    (Table~\ref{Tab:01}) Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text
    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text
    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.

    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text

    \begin{enumerate}
        \item this is item, use enumerate
        \item this is item, use enumerate
        \item this is item, use enumerate
    \end{enumerate}

    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows\vadjust{\pagebreak} that the
    above method Text Text Text Text Text Text Text Text Text Text
    Text Text.  \citealp{Boffelli03} might want to know about text
    text text text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text Text Text Text Text Text Text Text Text.
    \citealp{Boffelli03} might want to know about text text text text
    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text\break Text.

    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
    Text Text Text\vspace*{-10pt}

>>>>

    \section{Methods}

    \wfmash\ first applies a locality-sensitive hashing, from MashMap, to rapidly determine syntenic region
    boundaries between long DNA sequences. Then, a hierarchical implementation of the WFA allows computing the
    base-level global alignment of the identified mappings.

    \subsection{Approximate mapping}

    Each query sequence is broken into non-overlapping pieces of the requested length. These segments are then
    mapped using MashMap's sliding MinHash mapping algorithm~\citep{30423094}. We extended MashMap, fixing bugs
    and incorporating the robust winnowing \citep{Schleimer S. et al.  (2003)} in the minimizer downsampling.
    Robust sampling avoids taking too many minimizers in low-complexity substrings, yielding improvements in
    runtime and memory-usage without affecting accuracy~\citep{32657365}.

    %TODO THINGS ON THE FILTERING?
    %TODO THING ON THE SPLIT READ AND/OR THE MERGING?

    In addition to the segment length, the minimum segment estimated identity and the maximum number of
    mappings to report for each segment can be specified in the mapping process. These settings allow users
    to precisely define the mapping space to consider, specifying the characteristics of homologies to compute.
    Each mapping location is then used as a target for base-level alignment using a hierarchical implementation
    of the WFA.

    \subsection{Base-level alignment}

    The time and memory required to compute the base-level alignment increases quadratically with the sequence
    length. The WFA provides an efficient way to decrease the amount of computation required to obtain the
    optimal alignment between two sequences, reducing the cost to be quadratic in the alignment penalty score
    of the optimal alignment~\citep{32915952}. This means that the algorithm is very efficient in aligning
    similar homologous sequences (i.e., sequences with a low alignment penalty score), but high divergence
    genomes and/or noisy long reads can increase its memory and runtime costs.

    To avoid such limitation, wfmash applies a hierarchical WFA, exploiting the WFA to guide the alignment
    process, but keeping the largest alignment problem size small. Rather than directly aligning the whole
    sequences, it aligns them to each other in small pieces W-bps long by applying a global WFA alignment
    (Figure~1\vphantom{\ref{fig:1}}). The whole global alignment is then computed over the full
    dynamic-programming matrix (high order DP-matrix) at \textit{W}-bps resolution.
    Each cell in the high order DP-matrix corresponds to the alignment of a specific pair of fragments
    \textit{W}-bps long from the two sequences to align. To determine if each cell is a match, and then guiding the
    \textit{W}-bps resolution alignment, the global alignment using the standard WFA is performed between the
    two fragments.

    \begin{figure}[!tpb]%figure1
        \fboxsep=0pt\colorbox{gray}{
            \begin{minipage}[t]{235pt}
                \vbox to 100pt{\vfill\hbox to
                235pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
            \end{minipage}}
            %\centerline{\includegraphics{fig01.eps}}
        \caption{Generate a cool plot using R as a base to create a cool image.}\label{fig:1}
    \end{figure}

@@

    Finally, the \textit{W}-bps resolution traceback is applied to determine the set of base-level alignments
    on the optimal path in the high order DP-matrix. During the process, a further step is performed for
    refining the alignment. Indeed, inaccurate mapping estimation can lead to under-alignment at the beginning
    and the end of the aligned syntenic region. Therefore, edlib is applied by computing semi-global alignments
    to resolve the mapping boundaries.
    The hierarchical implementation requires only the memory to align a syntenic region at \textit{W}-bps resolution,
    limiting the runtime and the memory of the standard WFA by applying it to fragments \textit{W}-bps long.
    This approach is more flexible than using a fixed-width band (it effectively has a variable bandwidth), requires
    no heuristic seeding step, and can benefit from parallel exploration of the wavefront.
    %TODO 'this approach is more flexible than using a fixed-width band: Not sure about writing it. I would remove it, else we should demonstrate it.
    %TODO 'and can benefit from parallel exploration of the wavefront.' Can we?

    \section{Results}

    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.

@@

    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.
